Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper:fix count fractions

We also calculate the number of tuples used to produce each aggregate output.
The Count columns in \Cref{table:smape} show the percentage difference between the number of tuples in the aggregate for $\alpha = 0$ and $\alpha = 1$ and running the query on the imputed base table.
This shows that when optimizing for performance, not quality, many tuples are dropped.
Even in cases where the SMAPE reduction between $\alpha = 1$ and $\alpha = 0$ is small (\Cref{q2}, \Cref{q6}) the tuple count is significantly different.
In these cases, the aggregate value is not significantly impacted by the missing data. In particular, if values are missing uniformly at random,
the aggregate should not be affected.
However, if the missing data is biased then the aggregate will have a significant error.
This highlights a challenge for a user handling data imputation traditionally: it is unclear if the missing data will have a large or small negative impact on their analysis until they have paid the cost of running it.
By using \ProjectName{} this cost can be lowered significantly.

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations. To calculate SMAPE, \ProjectName{} results are compared to query results returned
    from executions with base table imputation. Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). Count shares show the number of results returned from each
    query as a percentage of the number of results returned when imputing on the base table.
    A lower count share reflects more potential for errors.}
\label{table:smape}
\end{table}

>>>>

We also calculate the number of tuples used to produce each aggregate output.
The count fraction columns in \Cref{table:smape} show the number of tuples in the aggregate for $\alpha = 0$ and $\alpha = 1$ as a fraction of the number of tuples
used when running the query on the imputed base table.
This shows that when optimizing for performance, not quality, many tuples are dropped.
Even in cases where the SMAPE reduction between $\alpha = 1$ and $\alpha = 0$ is small (\Cref{q2}, \Cref{q6}) the tuple count is significantly different.
In these cases, the aggregate value is not significantly impacted by the missing data. In particular, if values are missing uniformly at random,
the aggregate should not be affected.
However, if the missing data is biased then the aggregate will have a significant error.
This highlights a challenge for a user handling data imputation traditionally: it is unclear if the missing data will have a large or small negative impact on their analysis until they have paid the cost of running it.
By using \ProjectName{} this cost can be lowered significantly.

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations. To calculate SMAPE, \ProjectName{} results are compared to query results returned
    from executions with base table imputation. Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). The count fraction column shows the number of tuples used in calculating each aggregate
     as a fraction of the number of tuples used when running the same query after imputing on the base table.
    A lower count share reflects more potential for errors.}
\label{table:smape}
\end{table}
